Analysis of Programming Students' Prompts to Identify Patterns of Critical Thinking in Interactions with Generative AI \\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-08-26 paper/paper.tex
update

\section{Background}

>>>>

\section{Related Work}

The recent advancements in Generative Artificial Intelligence (GenAI) and its
use in programming courses have raised possibilities and concerns among
educators and researchers. The study of \cite{Yilmaz23} found that the main
benefit of using ChatGPT in programming learning is to provide providing fast
and mostly correct answers to questions, improving thinking skills, facilitating
debugging, and increasing self-confidence. In contrast, the study the same
appoint limitations such ask laziness, being unable to answer some questions,
or giving incomplete/incorrect answers, causing professional anxiety in students.
